%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,letterpaper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{etaremune}
\usepackage{doipubmed}
\usepackage[scale=0.85]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Aroon} % Your first name
\familyname{Chande} % Your last name

% All information in this block is optional, comment out any lines you don't need
%\title{Curriculum Vitae}
\address{}{Atlanta, GA 30318}
\mobile{(515) 981-6868}
\email{mail@aroonchande.com}
\homepage{aroonchande.com}{https://aroonchande.com} 
\homepageII{aroonchan.de}{https://www.aroonchan.de} 

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{Aug 2017 -- present}{\textit{(In progress)} Ph.D. - Bioinformatics}{\textsc{Georgia Institute of Technology}}{Atlanta}{GA}{}  
\cventry{Dec 2016}{Master of Science - Bioinformatics}{\textsc{Georgia Institute of Technology}}{Atlanta}{GA}{}  
\cventry{May 2015}{Bachelor of Science - Microbiology}{\textsc{University of Iowa}}{Iowa City}{IA}{}
\cventry{May 2013}{Bachelor of Science - Biology}{\textsc{University of Iowa}}{Iowa City}{IA}{}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\cventry{May 2016 -- Present}{Bioinformatics Scientist}{\textsc{Applied Bioinformatics Laboratory}}{\small IHRC Inc}{Atlanta, GA}{
\textit{\httplink{http://abil.ihrc.com}}
\begin{itemize}
\item Development and maintenance of analytics platforms 
\item Development and maintenance of custom bioinformatics databases
\item Teaching bioinformatics courses
\end{itemize}
\textit{Languages used: C++/Bash/Julia/PHP/Perl/Python/R/SQL}}

\cventry{May 2016 -- Present}{Graduate Student}{\textsc{Jordan Lab}}{\small Georgia Institute of Technology}{Atlanta, GA}{
\textit{\httplink{http://jordan.biology.gatech.edu}}
\begin{itemize}
\item Studying the effects of human ancestry on disease burden in Colombia and South America 
\item Teaching and administrating classes in the Bioinformatics Master’s program
\item Development of bacterial typing schemes in collaboration with the Centers for Disease Control and Prevention
\end{itemize}
\textit{Languages used: Bash/Perl/Python/R/SQL/PHP/Julia/Rust}}

\cventry{Aug 2015 -- May 2016}{Graduate Student Research}{\textsc{Hammer Lab}}{\small Georgia Institute of Technology}{Atlanta, GA}{
\textit{\httplink{http://www.hammerlab.biology.gatech.edu/}}
\begin{itemize}
\item Development and maintenance of \textit{vibriocholera.com} 
\item \textit{Vibrio cholerae} NGS bioinformatic analysis
\item Development of webtool for Type VI Secretion System annotation
\end{itemize}
\textit{Languages used: Bash/Perl/R/Python}}

\cventry{Dec 2011 -- July 2015}{Research Assistant}{\textsc{Apicella Lab}}{\small University of Iowa}{Iowa City, IA}{
\begin{itemize}
\item Development of expression and purification protocols for NMR and x-ray crystallography study of \textit{Haemophilus influenzae} nuclease in \textit{E. coli} 
\item Screening and data collection on crystallized nuclease in-house and Synchrotron radiation (4.2.2 beamline at ALS, Berkeley)
\item Biological assays for protein activity, targets and pH dependence
\item Biofilm, immunoassay and confocal microscopy
\end{itemize}
\textit{Languages used: Bash/Perl}}

\cventry{May 2011 -- May 2013}{Protein Crystallography Core Staff}{Carver College of Medicine}{Unversity of Iowa}{Iowa City, IA}{
\begin{itemize}
\item Contracted protein purification and characterization
\item User training for protein expression, purification and crystallization 
\item Development of custom protocols for in-house robotic liquid handlers
\end{itemize}
\textit{Languages used: Bash}}

\pagebreak
\section{Skills}
\subsection{Computational}
\cvitem{Proficient}{Bash, Perl, Python, R, Unix systems administration}
\cvitem{Familiar}{HTML/CSS, SQL}
\cvitem{Learning}{Julia, Rust}
\cvitem{NGS}{Whole Genome Sequencing (WGS), Whole Exome Sequences (WES), RNA-seq, microarray}
\cvitem{'Omics}{Transcriptomics, metabolomics, proteomics}
\cvitem{Development}{- Bacterial typing and identification tools using NGS data \newline- Automated systems for bioinformatics analysis and information management}
\cvitem{Robotics}{Liquid handlers (Mosquito, TECAN, Alchemist platform),  Microscopy (Rock Imager), and other programmable robotics platforms}
\subsection{Wet Lab}
\cvitem{Pathogens}{Collection and handling of biological samples}
\cvitem{FPLC/HPLC}{Affinity column, ionic / hydrophobic chromatography}
\cvitem{Microscopy}{Confocal, Light, SEM}
\cvitem{Genetics}{PCR and cell line mutant development}


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------


\section{Posters and Presentations}

\begin{etaremune}
\item \textbf{Chande, A.T.}, Norris, E.T., Moreno, A.M., Nagar, S.D., Rishishwar, L., O'Neal, K., Velex, S., Montes-Rodrigues, S., Torres, I., Medina-Rivas, M.A., Valderrama-Aguirre, A., Jordan, I.K., Gallo, J.E. (2018) Population pharmacogenomics for precision public health in Colombia.  S{\~a}o Paulo Advanced School on Vaccines,  S{\~a}o Paulo, Brazil.
\item \textbf{Chande, A.T.}, Wang, L., Rishishwar, L., Conley, A.B., Norris, E.T., Valderrama-Aguirre, A., Jordan, I.K. (2018) GlobAl Distribution of GEnetic Traits (GADGET): Exploring polygenic trait scores.  The American Society of Human Genetics, San Diego, California.
\item \textbf{Chande A.T.}, Conley, A.B., Rowell, J., Rishishwar, L., Norris, E.T.,  Mari{\~{n}}o-Ram{{\'i}}rez, L., Valderrama-Aguirre, A.,  Medina-Rivas, M., Jordan, I.K. (2018) ChocoGen: Genetic ancestry and health in the Colombian Pacific. Closing the genomics research gap, McGill University, Montreal, Canada.
\item \textbf{Chande, A.T.}, Rishishwar, L., Watve, S., Jordan, I.K., Hammer, B.K. (2015). Genomic analysis of Type VI secretion systems of \textit{Vibrio cholerae}. 10th International Conference on Bioinformatics, Atlanta, GA.
\end{etaremune}

\section{Awards and Honors}
\cventry{Summer 2016}{Graduate Research Award}{\textsc{Jordan lab}}{Georgia Institute of Technology}{Alanta, GA}{Reclassification of Non-typeable \textit{Haemophilus spp.}.}

\section{Publications}

\begin{etaremune}
\item Bernardy, E.E., Petit, R.A., Moller, A.G., Blumenthal, J.A., McAdam, A.J., Priebe, G.P., \textbf{Chande, A.T.}, Rishishwar, L., Jordan, I.K., Read, T.D.,  Goldberg, J.B. (2019) Whole-Genome Sequences of Staphylococcus aureus Isolates from Cystic Fibrosis Lung Infections. Microbiol Resour Announc 8 (3), e01564-18 \doi{10.1128/MRA.01564-18} \pubmed{30687841 }
\item Crisan C.V.*, \textbf{Chande A.T.*}, Williams K., Raghuram V., Rishishwar L., Steinbach G., Yunker P., Jordan I.K., Hammer B.K. (2019) Analysis of \textit{Vibrio cholerae} genomes using a novel bioinformatic tool identifies new, active Type VI Secretion System gene clusters. bioRxiv. \doi{10.1101/526723}
\item \textbf{Chande, A.T.}, Wang, L., Rishishwar, L., Conley, A.B., Norris, E.T., Valderrama-Aguirre, A., Jordan, I.K. (2018) GlobAl Distribution of GEnetic Traits (GADGET) web server: polygenic trait scores worldwide. Nucleic Acids Research. \doi{10.1093/nar/gky415}. \pubmed{29788182}
\item Cho, C.*, \textbf{Chande, A.T.*}, Gakhar, L., Hunt, J., Ketterer, M. R., Apicella, M. A. (2018) Characterization of a nontypeable Haemophilus influenzae Thermonuclease. PLoS One. \doi{10.1371/journal.pone.0197010}. \pubmed{29746527}
\item Medina-Cordoba, L.K., \textbf{Chande, A.T}, Rishishwar, L., Mayer, L.W., Mari{\~{n}}o-Ram{{\'i}}rez, L., Valderrama-Aguirre, L., Valderrama-Aguirre, A., Kostka, J.E, Jordan, I.K. (2018). Genome sequences of 15 Klebsiella spp. isolates from sugarcane fields in Colombia's Cauca Valley. Genome Announcements. \doi{10.1128/genomeA.00104-18}. \pubmed{29567732}
\item \textbf{Chande, A.T.}, Rowell, J., Rishishwar, L., Conley, A.B., Norris, E.T., Valderrama-Aguirre, A., Medina-Rivas, M., Jordan, I.K. (2017). Influence of genetic ancestry and socioeconomic status on type 2 diabetes in the diverse Colombian populations of Chocó and Antioquia. Scientific Reports. \doi{10.1038/s41598-017-17380-4}. \pubmed{29215035}
\item Dale, R., Gr{\"u}ning, B., Sj{\"o}din, A., Rowe, J., Chapman, B. A., Tomkins-Tinch, C. H., . . . \textbf{Chande, A. T.}, . . . K{\"o}ster, J. (2017). Bioconda: A sustainable and comprehensive software distribution for the life sciences. bioRxiv. \doi{10.1101/207092}
\item Espitia, H, \textbf{Chande, A. T.}, Jordan, I. K., Rishishwar, L. (2017). Method of sequence typing with in silico aptamers from a Next Generation Sequencing platform. Patent Pending.
\item Post, D. M. B., Sl{\"u}tter, B., Schilling, B., \textbf{Chande, A. T}., Rasmussen, J. A., Jones, B. D., . . . Apicella, M. A. (2017). Characterization of Inner and Outer Membrane Proteins from Francisella tularensis Strains LVS and Schu S4 and Identification of Potential Subunit Vaccine Candidates. mBio, 8(5). \doi{10.1128/mBio.01592-17}. \pubmed{29018123}
\item Topaz, N., Mojib, N., \textbf{Chande, A. T.}, Kubanek, J., \& Jordan, I. K. (2017). RampDB: a web application and database for the exploration and prediction of receptor activity modifying protein interactions. Database, 2017, bax067-bax067. \doi{10.1093/database/bax067}. \pubmed{29220456}
\item Norris, E. T., Rishishwar, L., Wang, L., Conley, A. B., \textbf{Chande, A. T.}, Dabrowski, A. M., . . . Jordan, I. K. (2017). Assortative mating on ancestry-variant traits in admixed Latin American populations. bioRxiv. \doi{10.1101/177634}
\item Post, D. M. B., Schilling, B., Reinders, L. M., D'Souza, A. K., Ketterer, M. R., Kiel, S. J., . . . \textbf{Chande, A. T.}, . . . Gibson, B. W. (2017). Identification and characterization of AckA-dependent protein acetylation in Neisseria gonorrhoeae. PLoS One, 12(6), e0179621. \doi{10.1371/journal.pone.0179621}. \pubmed{28654654}
\item Watve, S. S., \textbf{Chande, A. T.}, Rishishwar, L., Mari{\~{n}}o-Ram{{\'i}}rez, L., Jordan, I. K., \& Hammer, B. K. (2016). Whole-Genome Sequences of 26 Vibrio cholerae Isolates. Genome Announcements, 4(6). \doi{10.1128/genomeA.01396-16}. \pubmed{28007852}
\item Cho, C.*,\textbf{ Chande, A.*}, Gakhar, L., Bakaletz, L. O., Jurcisek, J. A., Ketterer, M., . . . Apicella, M. A. (2015). Role of the Nuclease of Nontypeable Haemophilus influenzae in Dispersal of Organisms from Biofilms. Infection and Immunity, 83(3), 950-957. \doi{10.1128/iai.02601-14}.  \pubmed{25547799}
\item Apicella, M.A., Gakhar, L., \textbf{Chande, A.T.}  Novel Thermonuclease from Haemophilus Influenzae and Uses Thereof in Industry and Scientific Research. Patent Pending.
\end{etaremune}

\section{Manuscripts in preparation}

\begin{etaremune}
\item \textbf{Chande, A.T.}, Rishshwar, L., Conley, A.B.m Valderrama-Aguirre, A., Medina-Rivas, M., Jordan, I.K. (2019) Ancestry effects on type 2 diabetes genetic risk inference in Hispanic/Latino populations. Genes.
\end{etaremune}

\end{document}
